Supplementary Materials: Inverse energy transfer in finite-temperature superfluid vortex reconnections

### 2024-11-25 supp-mat/supp-mat.tex
Update Supp Materials
Finish supplementary materials

\author{L. Galantucci}
\affiliation{Istituto per le Applicazioni del Calcolo ``M. Picone" IAC CNR, Via dei Taurini 19, 00185 Roma, Italy}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.4\textwidth]{schematic.png}
	\caption{Schematic diagram of the initial vortex configuration.}
	\label{fig:schematic}
\end{figure}

@@

In this Letter, we report all results using dimensionless units, where the characteristic length scale is $\tilde{\lambda} = D/D_0$, where $D^3=(1\times10^{-3}\mathrm{m})^3$ is the dimensional cube size, $D_0^3=(2\pi)^3$ is the non-dimensional cubic computational domain. The time scale is given by $\tilde{\tau}=\tilde{\lambda}^2\nu_n^0\nu_n$, where the non-dimensional viscosity $\nu_n^0$ resolves the small scales of the normal fluid. In these simulations, these quanties are $\tilde{\lambda}=1.59\times10^{-4}$m, $\nu_n^0=0.32$ and $\tilde{\tau}=0.366$s at $T=1.9K$ and $\tilde{\tau}=0.485$s at $T=2.1K$. We consider an initial configuration of two pairs of orthongal vortices, initialised as shown in the schematic of Fig.~\ref{fig:schematic}.

>>>>

\author{L. Galantucci}
\affiliation{Istituto per le Applicazioni del Calcolo ``M. Picone" IAC CNR, Via dei Taurini 19, 00185 Roma, Italy}
\affiliation{School of Mathematics, Statistics and Physics, Newcastle University, Newcastle upon Tyne, NE1 7RU, United Kingdom}

@@

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{schematic.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{schematic-2.png}
	\end{subfigure}
	\caption{Schematic diagram of the initial vortex configuration.}
	\label{fig:schematic}
\end{figure}

@@

In this Letter, we report all results using dimensionless units, where the characteristic length scale is $\tilde{\lambda} = D/D_0$, where $D^3=(1\times10^{-3}\mathrm{m})^3$ is the dimensional cube size, $D_0^3=(2\pi)^3$ is the non-dimensional cubic computational domain. The time scale is given by $\tilde{\tau}=\tilde{\lambda}^2\nu_n^0\nu_n$, where the non-dimensional viscosity $\nu_n^0$ resolves the small scales of the normal fluid. In these simulations, these quanties are $\tilde{\lambda}=1.59\times10^{-4}$m, $\nu_n^0=0.32$ and $\tilde{\tau}=0.366$s at $T=1.9K$ and $\tilde{\tau}=0.485$s at $T=2.1K$. We consider an initial configuration of two pairs of orthongal vortices, initialised as shown in the schematic of Fig.~\ref{fig:schematic}. The seperation between vortices in each pair $d$ is set to be $d_v=0.5$ in dimensionless units, and the shortest distance between pairs is $D_v=\sqrt{(\pi-d_v/2)^2+\pi^2}\approx 3.08$, so that $d_v\ll D_v$. The Lagrangian discretisation of vortex lines is $\Delta \xi = 0.025$ (a total of 1340 discretisation points across the 4 vortex lines), using a timestep of $\Delta t_{VF} = 5.56\times10^{-6}$. For the normal fluid, a total of $N=256^3$ mesh point were used, with a timestep of $\Delta t_{NS} = 45\Delta t_{VF}$.
